### 2021-04-13 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision Chapter 2

\subsection{Extensions}
In future iterations, the assertion syntax could be extended with some more features to improve usability and readability:
\begin{itemize}
\item \textbf{Local variables} to store, reuse and denominate computed values
\item \textbf{User-defined functions} to extract whole routines that can be reused in a single or even many assertion contracts, if defined as a module.
\item \textbf{if-else conditions} to adapt the domains of quantifications if certain conditions hold. The assertion that checks whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature: Firstly, the minimum of the given number has to be determined, however the \texttt{min}-function might not be supported as a built-in function by the target language (Tezos, for instance, does not support it). A solution for that could be to implement two branches in the program to handle each case. Secondly, if the greater of the two numbers is not evenly divided by the smaller one, the formula can be optimized by reducing the quantification domain by half to $(2 \le n \le \lfloor \frac{min(a,b)}{2} \rfloor)$, as a number cannot be evenly divided by any number between itself and its half \cite{bernhardt_veigel_2020}. With a syntax supporting an \texttt{if-else} control structure, the optimized assertion could look as follows:
\lstinputlisting[caption=Assertion syntax with if-else structures \cite{bernhardt_veigel_2020}, language=Assertion, label={lst:coprime}]{listings/coprime_ifelse.tza}
This feature is not included in the current version, because conditional domain restrictions make the translation from quantifiers to random generators or loops more complex. Aside from that, without the feature of variables and user-defined functions, the code is inflated significantly, thus causing increased origination cost.
\end{itemize}

>>>>

\subsection{Extensions}\label{sec:ext}
In future iterations, the assertion syntax could be extended with some more features to improve usability and readability:
\begin{itemize}
\item \textbf{Local variables} to store, reuse and denominate computed values
\item \textbf{User-defined functions} to extract whole routines that can be reused in a single or even many assertion contracts, if defined as a module.
\item \textbf{if-else conditions} to adapt the domains of quantifications if certain conditions hold. The assertion that checks whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature: Firstly, the minimum of the given number has to be determined, however the \texttt{min}-function might not be supported as a built-in function by the target language (Tezos, for instance, does not support it). A solution for that could be to implement two branches in the program to handle each case. Secondly, if the greater of the two numbers is not evenly divided by the smaller one, the formula can be optimized by reducing the quantification domain by half to $(2 \le n \le \lfloor \frac{min(a,b)}{2} \rfloor)$, as a number cannot be evenly divided by any number between itself and its half \cite{bernhardt_veigel_2020}. With a syntax supporting an \texttt{if-else} control structure, the optimized assertion could look as follows:
\lstinputlisting[caption=Assertion syntax with if-else structures \cite{bernhardt_veigel_2020}, language=Assertion, label={lst:coprime}]{listings/coprime_ifelse.tza}
This feature is not included in the current version, because conditional domain restrictions make the translation from quantifiers to random generators or loops more complex. Aside from that, without the feature of variables and user-defined functions, the code is inflated significantly, thus causing increased origination cost.
\end{itemize}
